---
title: "Alcohol vs Seat choice"
author: "Nadya Mitwasi"
date: "Spring 2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r include=FALSE}
require(tidyverse)
require(tigerstats)
davisdata <- read.csv(file="UCDavis.csv")
```
## Our Goal is to answer this question Is there a difference between the alcohol consumed between the row
## you choose to sit in??

$H_0$: the null hypothesis is that there is no difference between the alcohol consumed between the row you choose to sit in ??
  
$H_A$: the alternative hypothesis is that there is a difference between the alcohol consumed between the row you choose to sit in ??

## Now with ggplot - first select the basic data

```{r}
basicCN <- ggplot(davisdata,aes(y=alcohol,x=Seat))
```
## Now add in boxplot

```{r}
basicCN + geom_boxplot()
```
  
  Accordingly, the total alcohol intake of people who choose to sit on the back seat at 9.6 percent tends to be slightly above that of those who stood in the front at 1.8 percent on the medium of the alcohol consumption and 3.28 percent on the center of the back seat.
  
### get fancy  

```{r}
basicCN + geom_boxplot(notch=TRUE,outlier.color = "red") + stat_boxplot(geom ='errorbar') + labs(title="Fancy notch boxplot \n with 2 lines")
```

## Numerical Summarys 

## Inferential Tests

## Conclusions


